Patchwork: Incremental Computation for Static Analysis

### 2018-10-13 paper.tex
Fix analysis trace diagram by removing spurious edge
first draft of analysis loop: show calls to 'update', to 'push', and to 'pop' in the loop

@@

\begin{table}[]
  \centering
  \newcommand{\location}{\tikz\draw[green!65!black,fill=green!65!black] (0,0) circle (.4ex);}
  \def\arraystretch{2}
    \begin{tabular}{r|l|ccl}
        \# & Program Location & \multicolumn{3}{l}{Analysis State Progression} \\
        \midrule
        1 & \texttt{x = 10;\location} &\quad&$\{\}$\tikzmark{1a} & \\
        \hline
        2 & \texttt{y = 0;\location} &$\bot$\quad& $\{x+y\leq10\}$\tikzmark{2a} & \hspace{1em}$\{x+y\leq10\}$\tikzmark{2b}\\
        \hline
        3 & \texttt{while(x > 0)\{\location} &$\bot$\quad& $\{x+y\leq10\}$\tikzmark{3a} & \tikzmark{3b}\\
        \hline
        4 & \quad\texttt{x--;\location} &$\bot$\quad&  $\{x+y\leq9\}$\tikzmark{4a}& \\
        \hline
        5 & \quad\texttt{if(*) \{y++;\location\}} &$\bot$\quad&$\{x+y\leq10\}$\tikzmark{5a}& \\
        \hline
        6 & \quad\texttt{else \{$\epsilon$;\location\}} &$\bot$\quad& $\{x+y\leq9\}$\tikzmark{6a} & \\
        \hline
        7 & \location\texttt{\}} &$\bot$\quad& $\{x+y\leq10\}$\tikzmark{7a} & \tikzmark{7b}\\
        \hline
%        8 & \qquad$\epsilon$ & $x+y\leq9$& \\
%        \hline
        8 & \location~\texttt{assert(x + y $\le$ 10)} &$\bot$\quad& $\{x+y\leq10\}$\tikzmark{8a} & \hspace{1em}$\{x+y\leq10\}$\tikzmark{8b}\\
    \end{tabular}

@@

    \begin{tikzpicture}[overlay,remember picture, shorten >=-3pt]
      \coordinate (1a) at ([xshift=-0.46em]pic cs:1a) ;
      \coordinate (2a) at (pic cs:2a);
      \coordinate (3a) at (pic cs:3a);
      \coordinate (4a) at (pic cs:4a);
      \coordinate (5a) at (pic cs:5a);
      \coordinate (6a) at (pic cs:6a);
      \coordinate (7a) at (pic cs:7a);
      \coordinate (8a) at (pic cs:8a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a) -- ([yshift = \abovetext]1a|-2a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-2a) -- ([yshift = \abovetext]1a|-3a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-3a) -- ([yshift = \abovetext]1a|-4a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-4a) -- ([yshift = \abovetext]1a|-5a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-4a)
      to [out=270,in=90] ([xshift=0.6em,yshift=0.2em] pic cs:5a)
      to [out=270,in=90] ([yshift = \abovetext]1a|-6a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-5a)
      to [out=270,in=90] ([xshift=-5.25em,yshift=0.25em] pic cs:6a)
      to [out=270,in=90] ([yshift = \abovetext]1a|-7a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-6a) -- ([yshift = \abovetext]1a|-7a);
      \draw[->, blue!75!black,rounded corners=4pt] ([yshift=4pt,xshift=1pt] pic cs:7a) -| ([xshift=-1pt] pic cs:3b) |- ([xshift=-5.5em, yshift=3pt]pic cs:2b);
      \draw[->, blue!75!black,rounded corners=4pt] ([yshift=4pt,xshift=1pt] pic cs:7a) -| ([yshift=-5pt, xshift=-1pt] pic cs:7b) |- ([xshift=-5.5em, yshift=3pt]pic cs:8b);
      \draw[->, blue!75!black,rounded corners=3pt] ([yshift=3pt,xshift=-5.25em] pic cs:2a) -| ([xshift=-5.65em,yshift=0.35em] pic cs:6a) |- ([yshift=3pt,xshift=-5.5em] pic cs:8a);
    \end{tikzpicture}

>>>>

\begin{figure}
\begin{lstlisting}
type Q
type Inv
type VisitRes = NoChange | Change Inv

let visitloc : Inv -> Loc -> VisitRes =
  lam inv loc. 
    ...(elided program analysis logic)...
    ...
    ...   let inv' = update inv name loc absstate ;
    ...   Change inv'
    ...
    ...(elided program analysis logic)...

letrec loop : Inv -> Q -> Inv =
  lam inv q.
    match pop q with
      None -> inv
      Some q loc ->
         match visitloc loc inv with
           NoChange -> loop inv q
           Change inv -> loop inv (push q (succof loc))    
\end{lstlisting}
\end{figure}

@@

\begin{table}[]
  \centering
  \newcommand{\location}{\tikz\draw[green!65!black,fill=green!65!black] (0,0) circle (.4ex);}
  \def\arraystretch{2}
    \begin{tabular}{r|l|ccl}
        \# & Program Location & \multicolumn{3}{l}{Analysis State Progression} \\
        \midrule
        1 & \texttt{x = 10;\location} &\quad&$\{\}$\tikzmark{1a} & \\
        \hline
        2 & \texttt{y = 0;\location} &$\bot$\quad& $\{x+y\leq10\}$\tikzmark{2a} & \hspace{1em}$\{x+y\leq10\}$\tikzmark{2b}\\
        \hline
        3 & \texttt{while(x > 0)\{\location} &$\bot$\quad& $\{x+y\leq10\}$\tikzmark{3a} & \tikzmark{3b}\\
        \hline
        4 & \quad\texttt{x--;\location} &$\bot$\quad&  $\{x+y\leq9\}$\tikzmark{4a}& \\
        \hline
        5 & \quad\texttt{if(*) \{y++;\location\}} &$\bot$\quad&$\{x+y\leq10\}$\tikzmark{5a}& \\
        \hline
        6 & \quad\texttt{else \{$\epsilon$;\location\}} &$\bot$\quad& $\{x+y\leq9\}$\tikzmark{6a} & \\
        \hline
        7 & \location\texttt{\}} &$\bot$\quad& $\{x+y\leq10\}$\tikzmark{7a} & \tikzmark{7b}\\
        \hline
        8 & \location~\texttt{assert(x + y $\le$ 10)} &$\bot$\quad& $\{x+y\leq10\}$\tikzmark{8a} & \\
    \end{tabular}

@@

    \begin{tikzpicture}[overlay,remember picture, shorten >=-3pt]
      \coordinate (1a) at ([xshift=-0.46em]pic cs:1a) ;
      \coordinate (2a) at (pic cs:2a);
      \coordinate (3a) at (pic cs:3a);
      \coordinate (4a) at (pic cs:4a);
      \coordinate (5a) at (pic cs:5a);
      \coordinate (6a) at (pic cs:6a);
      \coordinate (7a) at (pic cs:7a);
      \coordinate (8a) at (pic cs:8a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a) -- ([yshift = \abovetext]1a|-2a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-2a) -- ([yshift = \abovetext]1a|-3a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-3a) -- ([yshift = \abovetext]1a|-4a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-4a) -- ([yshift = \abovetext]1a|-5a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-4a)
      to [out=270,in=90] ([xshift=0.6em,yshift=0.2em] pic cs:5a)
      to [out=270,in=90] ([yshift = \abovetext]1a|-6a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-5a)
      to [out=270,in=90] ([xshift=-5.25em,yshift=0.25em] pic cs:6a)
      to [out=270,in=90] ([yshift = \abovetext]1a|-7a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-6a) -- ([yshift = \abovetext]1a|-7a);
      \draw[->, blue!75!black,rounded corners=4pt] ([yshift=4pt,xshift=1pt] pic cs:7a) -| ([xshift=-1pt] pic cs:3b) |- ([xshift=-5.5em, yshift=3pt]pic cs:2b);
%      \draw[->, blue!75!black,rounded corners=4pt] ([yshift=4pt,xshift=1pt] pic cs:7a) -| ([yshift=-5pt, xshift=-1pt] pic cs:7b) |- ([xshift=-5.5em, yshift=3pt]pic cs:8b);
      \draw[->, blue!75!black,rounded corners=3pt] ([yshift=3pt,xshift=-5.25em] pic cs:2a) -| ([xshift=-5.65em,yshift=0.35em] pic cs:6a) |- ([yshift=3pt,xshift=-5.5em] pic cs:8a);
    \end{tikzpicture}
